Naming Anonymous JavaScript Functions

### 2011-04-13 papers/splash-wavefront2011/sigplanconf-template.tex
first 5 sections + table 7 were updated.

\conferenceinfo{WXYZ '05}{date, City.} 
\copyrightyear{2011} 
\copyrightdata{[to be supplied]}

@@

\begin{abstract}
JavaScript developers create and call functions; they use functions to construct objects. JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations. However, developers need not specify names for functions.  
 Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
By studying examples from these JavaScript projects, we propose Static Function-Object Consumption, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.  We applied our approach to these same JavaScript projects and the results are very promising.
\end{abstract}

@@

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

@@

\begin{table}

\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l |}
  \hline
   Project & Ver. & Description & Total & Named \\ 
  \hline 
   Closure &  & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All & N/A & N/A & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
\label{js-functions} 
\end{table}

@@

A JavaScript function can be defined with the {\small\texttt{function}} operator or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}. The {\small\texttt{function}} operator can appear in a function declaration, function expression, or function statement (the latter form is available in Firefox but not part of a standard).  Of these forms, only the function declaration requires a function name and the {\small\texttt{Function}} constructor has no mechanism to name the function.  In other words, JavaScript developers can define functions with or without function names.

@@

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

\begin{figure}[htp]

@@

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call). A constructor is a regular JavaScript function. Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{Foo}} and {\small\texttt{Bar}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{Baz.Bar}} class for {\small\texttt{bar}} as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{Foo}} and {\small\texttt{Bar}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of one of them({\small\texttt{main}}) correctly. For the second function (line 22), it shows \textit{anonymous}, and for the third function (line 12), it gives a wrong name, {\small\texttt{foo}}. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows {\small\texttt{main}} as the name of last function(line 12) which is the name of its enclosing function.
In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

@@

%Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.

@@

We instead propose an almost automated approach for naming all functions by analyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

@@

Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
zero to many {\small\texttt{Function}} objects can be created from the same definition. 
Two function objects which are created from the same function body may have different object properties added at runtime. They also may have different enclosing scopes and therefore different behaviors.  Thus our first 
decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?

For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects. The  names of these properties inform the developer about the role of the function in the actions of the object.  To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation). Our function names serve to recall or summarize that source or documentation for the developer. Therefore we seek to name the source, the content between the curly braces known as the {\textit{FunctionBody}} in the standard\cite{ECMA}.

@@

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

@@

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We'll ignore nesting of function scopes in the analysis to avoid taking on too much at one time.

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12\\ 
  \hline 
   Closure       & 23(0.3\%)  & 0  & 8466(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%) & 16(0.2\%) & 0  & 43(0.5\%) & 365(4\%)\\ 
  \hline 
   DOJO          & 9601(61\%) & 7  & 1765(11\%) & 21 & 24 & 2  & 1 & 1151(7\%) & 476(3\%) & 2  & 175(1\%) & 2641(17\%) \\ 
  \hline 
   ExtJS         & 30221(83\%) & 0  & 1476(4\%)  & 3  & 40 & 9  & 0 & 859(2\%) & 788(2\%) & 180  & 517(1\%) & 2439(7\%) \\ 
  \hline 
   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 2  & 0  & 0 & 17(0.4\%) & 7(0.2\%) & 2  & 6(0.2\%) & 148(5\%) \\ 
  \hline 
   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 10(2\%)   & 0  & 0        & 86(21\%)  \\ 
  \hline 
   MochiKit      & 1080(59\%) & 10  & 385(21\%)  & 0  & 4  & 0  & 0 & 110(6\%) & 18(1\%)  & 0  & 41(2\%)  & 181(10\%) \\ 
  \hline 
   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 20  & 14(2\%)  & 85(13\%) \\ 
  \hline 
   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 1  & 8(2\%)   & 70(16\%) \\ 
  \hline 
   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 21  & 9(1\%)   & 139(15\%) \\ 
  \hline 
   YUI           & 14154(66\%) & 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%) & 172(1\%) & 0  & 95(0.5\%) & 4004(19\%)\\ 
  \hline 
   All           & 58776(65\%)& 24 & 14568(16\%)& 28 & 180& 19 & 1 & 3514(4\%)& 1597(2\%)& 226  & 908(1\%) & 10072(11\%) \\ 
  \hline 
  \end{tabular}
}
\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
\label{function-type-count} 
\end{table*}

%     and extracting the initial name used for the function object after its creation. 
%In the third subsection we discuss qualities we expect from an automatically created function name.

\subsection{Case 1: Object Property Initializer}
 This case usually appears when developers try to group a set of functions in a new object. A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor. This structure resembles the class structure in traditional object-oriented languages. When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype. This structure is also used  when the owner object is a shared object with a set of utility functions.

@@

\subsection{Case 2: Entry in an Array Literal}
\label{sec:arrayLiteral}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only two have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI:
\begin{verbatim}
_attach: function (el, notifier, delegate) {
  if (Y.DOM.isWindow(el)) {
    return Event._attach([type, function (e) {
         notifier.fire(e);
    }, el]);
  }
}
\end{verbatim}
(The example is nested in more function definitions we do not show here). The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

@@

Following the model from Case 1, we expect a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression. (This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier). Here is a simple example from the Closure project: 
\begin{verbatim}
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{verbatim}
 These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we can't know the value of \verb|this| while parsing.

@@

\subsection{Case 5: Property Assignment With  Property Name Variable}
Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't (usually) statically compute the string to use as a property identifier.
The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
 name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}. Unlike the previous two cases, we
don't have a specific property name.  Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
\begin{figure*}[htp]
\begin{verbatim}
jQuery.each( "ajaxStart ajaxStop ajaxComplete ajaxError".split(" "), function( i, o ) {
    jQuery.fn[o] = function( f ) {
        return this.bind(o, f);
    };
});
\end{verbatim}
\caption{An example of functions passed as arguments to a function (row 11 in Table~\ref{table:function-types} and (the inner definition) an example of a 
function assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}. The function is from the jQuery library but simplified to fit on the page. }
\label{fig:jQueryEach}
\end{figure*}

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
\label{sec:propexpressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
\begin{verbatim}
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{verbatim}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 9: Anonymous Functions Immediately Called}
Calling functions objects just after their creations is a common pattern in JavaScript. For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example. 
\begin{figure}[htp]
\begin{verbatim}
Y.ClassNameManager = function () {

 var sPrefix    = CONFIG[CLASS_NAME_PREFIX],
   sDelimiter = CONFIG[CLASS_NAME_DELIMITER];

    return {
       getClassName: Y.cached(function () {
          var args = Y.Array(arguments);
          if (args[args.length-1] !== true) {
              args.unshift(sPrefix);
          } else {
              args.pop();
          }
          return args.join(sDelimiter);
      })
    };
}();
\end{verbatim}
\label{fig:classnamemanager}
\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
\end{figure}

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we can't use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.

>>>>

\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portlant, Oregon, USA.} 
\copyrightyear{2011} 
\copyrightdata{[to be supplied]}

@@

\begin{abstract}
JavaScript developers create and call functions; they use functions to construct objects. JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations. However, developers need not to specify names for functions.  
 Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
By studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions. We applied our approach to 90000 anonymous functions appeared in the analyzed JavaScript project. The approach is successful in naming more than 99\% (91\% are unique in file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.

\end{abstract}

@@

\section{Introduction}
The unique and important role of JavaScript in web programming is undeniable. Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site. This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}. It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards2}. There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.

@@

@@

A JavaScript function can be defined with the \verb|function| operator or the \verb|Function| constructor (i.e., \verb|new Function(| \verb|args, source)|) \cite{ECMA}. The \verb|function| operator can appear in a function declaration, function expression, or function statement (the latter form is available in Firefox but not part of a standard).  Of these forms, only the function declaration requires a function name and the \verb|Function| constructor has no mechanism to name the function.  In other words, JavaScript developers can define functions with or without function names.

@@

\begin{table}%[htp]

\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l |}
  \hline
   Project & Ver. & Description & Total & Named \\ 
  \hline 
   Closure & r683 & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & All Projects & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
\label{js-functions} 
\end{table}

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor. Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call). A constructor is a regular JavaScript function. Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.

\begin{figure}%[htp]

@@

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|. However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. \verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of first function (\verb|main|) correctly. For the second function (line 22), it shows \verb|anonymous|, and for the last function (line 12), it gives a wrong name, \verb|foo|. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows \verb|main| as the name of last function(line 12) which is the name of another function (the enclosing function at line 9). In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

@@

%Two other pieces of information which are important at function calls are \verb|this}} and argument values. In JavaScript, \verb|this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The \verb|this}} value is missed in both views. The \verb|arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.

@@

We instead propose an automated approach for naming anonymous functions by analyzing the source code. Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.

@@

Once a statement which defines a function is evaluated, a new \verb|Function| 
object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
zero to many \verb|Function| objects can be created from the same definition. 
Two function objects which are created from the same function body may have different object properties added at runtime. They also may have different enclosing scopes and therefore different behaviors.  Thus our first 
decision: do we try to name the \verb|Function| objects or the source that defines them?

For the common use cases, the different \verb|Function| objects are bound to one or more properties of objects. The  names of these properties inform the developer about the role of the function in the actions of the object.  To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation). Our function names serve to recall or summarize that source or documentation for the developer. Therefore we seek to name the source, the content between the curly braces known as the {\textit{FunctionBody}} in the standard\cite{ECMA}.

@@

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate objects, properties and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

@@

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.

\begin{table}[htp]
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

\begin{table*}[htp]
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l |}
  \hline
     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12\\ 
  \hline 
   Closure       & 23(0.3\%)  & 0  & 8466(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%) & 16(0.2\%) & 0  & 43(0.5\%) & 365(4\%)\\ 
  \hline 
   DOJO          & 9601(61\%) & 7  & 1765(11\%) & 21 & 24 & 2  & 1 & 1151(7\%) & 476(3\%) & 2  & 175(1\%) & 2641(17\%) \\ 
  \hline 
   ExtJS         & 30221(83\%) & 0  & 1476(4\%)  & 3  & 40 & 9  & 0 & 859(2\%) & 788(2\%) & 180  & 517(1\%) & 2439(7\%) \\ 
  \hline 
   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 2  & 0  & 0 & 17(0.4\%) & 7(0.2\%) & 2  & 6(0.2\%) & 148(5\%) \\ 
  \hline 
   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 10(2\%)   & 0  & 0        & 86(21\%)  \\ 
  \hline 
   MochiKit      & 1080(59\%) & 10  & 385(21\%)  & 0  & 4  & 0  & 0 & 110(6\%) & 18(1\%)  & 0  & 41(2\%)  & 181(10\%) \\ 
  \hline 
   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 20  & 14(2\%)  & 85(13\%) \\ 
  \hline 
   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 1  & 8(2\%)   & 70(16\%) \\ 
  \hline 
   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 21  & 9(1\%)   & 139(15\%) \\ 
  \hline 
   YUI           & 14154(66\%) & 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%) & 172(1\%) & 0  & 95(0.5\%) & 4004(19\%)\\ 
  \hline 
   All           & 58776(65\%)& 24 & 14568(16\%)& 28 & 180& 19 & 1 & 3514(4\%)& 1597(2\%)& 226  & 908(1\%) & 10072(11\%) \\ 
  \hline 
  \end{tabular}
}
\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
\label{function-type-count} 
\end{table*}

%     and extracting the initial name used for the function object after its creation. 
%In the third subsection we discuss qualities we expect from an automatically created function name.
\subsection{Case 1: Object Property Initializer}
 This case usually appears when developers try to group a set of functions in a new object. A common case is grouping a set of functions in the \verb|prototype| property of the constructor. This structure resembles the class structure in traditional object-oriented languages. When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype. This structure is also used  when the owner object is a shared object with a set of utility functions.

@@

\subsection{Case 2: Entry in an Array Literal}
\label{sec:arrayLiteral}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only three have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI \footnote[3]{The example is nested in more function definitions we do not show here.}:
%\begin{verbatim}
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  _attach: function (el, notifier, delegate) {
    if (Y.DOM.isWindow(el)) {
      return Event._attach([type, function (e) {
        notifier.fire(e);
      }, el]);
    }
  }
\end{lstlisting}
%\end{verbatim}
The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

@@

Following the model from Case 1, we expect a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}. Here is a simple example from the Closure project: 
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{lstlisting}

 These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.

@@

\subsection{Case 5: Property Assignment With  Property Name Variable}
Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we cannot (usually) statically compute the string to use as a property identifier.
The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
 name in the cases we examined was generic name like \verb|o| or \verb|item|. Unlike the previous two cases, we
do not have a specific property name.  Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
\begin{figure}[htp]
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  jQuery.each("ajaxStart ajaxStop ajaxComplete ajaxError"
    .split(" "), function( i, o ) {
       jQuery.fn[o] = function( f ) {
         return this.bind(o, f);
       };
  });
\end{lstlisting}
\caption{An example of a function (the inner definition) assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}) and an example of 
functions passed as arguments to a function (row 11 in Table~\ref{table:function-types}). The function is from the jQuery library but simplified to fit on the page. }
\label{fig:jQueryEach}
\end{figure}

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
\label{sec:propexpressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., \verb|condition?"prop1":"prop2"|, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{lstlisting}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 9: Anonymous Functions Immediately Called}
Calling function objects just after their creations is a common pattern in JavaScript. For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example. 
\begin{figure}[htp]
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  Y.ClassNameManager = function () {
    var sPrefix = CONFIG[CLASS_NAME_PREFIX],
    sDelimiter = CONFIG[CLASS_NAME_DELIMITER];
    return {
      getClassName: Y.cached(function () {
        var args = Y.Array(arguments);
        if (args[args.length-1] !== true) {
          args.unshift(sPrefix);
        } else {
          args.pop();
        }
        return args.join(sDelimiter);
      })
    };
  }();
\end{lstlisting}
\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
\label{fig:classnamemanager}
\end{figure}

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
